### 2021-06-30 paper.Rmd
save; introduction is being worked on

Anticlustering is useful in many tasks surrounding research work in psychology. For example, anticlustering can be used to split a test into parts of equal difficulty [@gierl2017], to assign students to work groups [@baker2002] or when assigning stimuli to experimental conditions [@lahl2006]. For an overview of anticlustering applications in psychology and other areas, see @brusco2019 and @papenberg2020. Solving anticlustering problems "by hand" is a tedious and time-consuming task, and the quality of manual group assignment is usually suboptimal. Fortunately, these problems can be formalized as mathematical optimization problems [e.g., @brusco2019; @spath1986; @baker2002; @fernandez2013] and accessible open source software solutions to tackling these problems exist [@papenberg2020].

---

**TODO; hier weitermachen**

Several anticlustering objectives are based pairwise dissimilarity ratings; the most prominent criterion of this kind is the *diversity*, which is the total sum of dissimilarities between any elements within the same group. Another important criterion based on pairwise dissimilarities is the dispersion, which is the minimum dissimilarity between any two items in the same group [@fernandez2013; @brusco2019]. Maximizing the dispersion increases the within-group heterogeneity by ensuring that any two elements as dissimilar as possible from each other.

>>>>

Anticlustering is useful in many tasks surrounding research work in psychology. For example, anticlustering can be used to split a test into parts of equal difficulty [@gierl2017], to assign students to work groups [@baker2002] or when assigning stimuli to experimental conditions [@lahl2006]. For an overview of anticlustering applications in psychology and other areas, see @brusco2019 and @papenberg2020. Solving anticlustering problems "by hand" is a tedious and time-consuming task, and the quality of manual partitioning is usually suboptimal. Fortunately, these problems can be formalized as mathematical optimization problems [e.g., @brusco2019; @spath1986; @baker2002; @fernandez2013] and accessible open source software solutions to tackling these problems exist [@papenberg2020].

Several anticlustering objectives exist that differ in the assumed input data and their mathematical definition of cluster similarity. Some anticlustering objectives are based pairwise dissimilarity ratings; the most prominent criterion of this kind is the *diversity*, which is the total sum of dissimilarities between any elements within the same group. Another important criterion based on pairwise dissimilarities is the dispersion, which is the minimum dissimilarity between any two items in the same group [@fernandez2013; @brusco2019]. Maximizing the dispersion increases the within-group heterogeneity by ensuring that any two elements as dissimilar as possible from each other.
